\section{Currently Supported Types}

\begin{itemize}

	\item Bool: represents the truth values true and false. Encoded within a byte: 1 for true, 0 for false. Represented in Go by type bool.
	\item Integer: u?int(8|16|32|64). Each represents the set of n-bit signed/unsigned integers.
Encoded in n-bit little-endian; an n-bit type is always encoded using n bits. Represented in
Go by types u?int(8|16|32|64).
	\item Floating point types: float(32|64). Each represents the set of n-bit floating point numbers.
Encoded in little-endian IEE-754. Represented in Go by types float(32|64).

	\item string: represents the set of Unicode strings. Encoded using UTF-8. The length in bytes 
l of the UTF-8 encoded string is sent first as a uint32, followed by the l bytes themselves.
Represented in Go by type string.

	\item tuple: an ordered list of elements of a given type. The length in elements l of a tuple
value is sent as a uint32, followed by l encoded values of the tuple's element type.
Represented in Go by array and slice types.

	\item pointer: a reference to a value of a given type. The way a pointer value is classified and encoded
depends on whether or not the pointer is nil and whether it has already been encoded as part
of a larger value (e.g. as part of a circular value). If a pointer value is nil, PNIL is
encoded within a byte and encoding is complete. If a pointer value has been encoded before as
part of the same, larger value, PIDX is encoded within a byte, followed by the index of the
previously encoded value. Otherwise, PVAL is encoded within a byte, followed by the encoded value
that the pointer references. Represented in Go by pointer types.

	\item struct: a composite type containing named fields with specified types. Names are ignored when
sending or receiving structs; a struct is sent by encoding each field in the order specified by
the type of the structure. Represented in Go by struct types. In order to encode or decode a
struct, all fields must be exported.

	\item dict: a map of keys to values. Not currently implemented.

	\item smart pointer: a reference to a value which may or may not be in memory. Not currently implemented.

	\item any: a reference to a value of any type. Sent by encoding the hash for the type of the concrete
value references as a Tuple, followed by the encoded value that the any references. Represented
in Go by interface types. In order to encode or decode a value contained in an interface,
the hash for the value's type must have been registered.

\end{itemize}
