\section{packetEncoder.h}
The data structure defined here is \emph{packetEncoder}. It contains:

\begin{itemize}
\item EtnBufferEncoder encoder
\item Packet  *packet
\item uint32\_t totalLength
\item bool packetSent
\item Connection *connection
\end{itemize}
The functions declared here are:

\begin{itemize}

\item\emph{PacketEncoder *packetEncoderNew(void)}\\
This function creates a new, blank packetEncoder. Must be reset before use. The definition is inside \emph{packetEncoder.c}.

\item\emph{void packetEncoderReset(PacketEncoder *e, Connection *c, uint32\_t totalLength)}\\
This function resets the packetEncoder. The definition is inside \emph{packetEncoder.c}.

\item\emph{int packetEncoderWrite(EtnEncoder *\_e, uint8\_t *data, uint32\_t length)}\\
This function writes data to a packet. Inside \emph{packetEncoder.c} there is the definition of \emph{\_packetEncoderWrite} which is \emph{static}. By definition of \emph{static} keyword, a function declared \emph{static} cannot be seen outside the file it was defined in. So, if they are the same function, it is not clear why it is also defined in header file.

\item\emph{void packetEncoderFlush(EtnEncoder *e)}\\
This function flushes packet encoder, sending the packet as the final fragment. Inside \emph{packetEncoder.c} there is the definition of \emph{\_packetEncoderFlush} which is static. By definition of \emph{static} keyword, a function declared \emph{static} cannot be seen outside the file it was defined in. So, if they are the same function, it is not clear why it is also defined in header file.

\end{itemize}